Singletons

### 2020-02-07 analysis/reports/singletons.Rmd
testing one idea

>>>>

```{r remove high skew}

ggplot(data = filter(singletons_effect), aes(x = skewdiff)) +
  geom_histogram() +
  theme_bw()
ggplot(data = filter(singletons_effect, skew_percentile_FALSE <= 75), aes(x = skewdiff)) +
  geom_histogram() +
    geom_histogram(data = singletons_effect, alpha = .2) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") +
  geom_vline(xintercept = 0)

```
With the possible exception of gentry, removing the highly skewed sites does not recenter the difference on 0. So the reason bbs and fia have so many down below 0 is not "shifting below zero is only possible if skew starts out lowish; bbs and fia are the only ones with a lot of intermediate starting skew values; if we constrain the others to only their intermediate starting skew values, they too will have proportionally lots below zero".
